---
title: "Data 607 Final Project"
author: "Melissa Bowman"
date: "2022-12-04"
output: html_document
---

### Load libraries.
```{r libraries, results='hide',message=FALSE}
library(rvest)
library(tidyverse)
```


### Webscraping
Using rvest take link and read html. 
```{r}
# Webpage
link = "https://shop.tcgplayer.com/price-guide/pokemon/swsh12-silver-tempest"
link_trainer = "https://shop.tcgplayer.com/price-guide/pokemon/swsh12-silver-tempest-trainer-gallery"

#Reading_html
page = read_html(link)
page_trainer = read_html(link_trainer)
```


### Pulling from html link to create first dataframe
```{r}
name = page %>% html_nodes(".product .cellWrapper") %>% html_text()
price = page %>% html_nodes(".marketPrice .cellWrapper") %>% html_text()
id = page %>% html_nodes(".number .cellWrapper") %>% html_text()
rarity = page %>% html_nodes(".rarity .cellWrapper") %>% html_text()

silver_tempest_price_guide = data.frame(name, price, id, rarity, stringsAsFactors = FALSE)
```


### Pulling from html link to create second dataframe
```{r}
name = page_trainer %>% html_nodes(".product .cellWrapper") %>% html_text()
price = page_trainer %>% html_nodes(".marketPrice .cellWrapper") %>% html_text()
id = page_trainer %>% html_nodes(".number .cellWrapper") %>% html_text()
rarity = page_trainer %>% html_nodes(".rarity .cellWrapper") %>% html_text()

silver_tempest_trainer_price_guide = data.frame(name, price, id, rarity, stringsAsFactors = FALSE)
```

### Merging the two data frame together to get full list of Silver Tempest
```{r}
silver_tempest_full = rbind(silver_tempest_price_guide, silver_tempest_trainer_price_guide)
```

### Tidying of silver_tempest_full data frames before statistical analysis.
```{r}
silver_tempest_full <- silver_tempest_full %>%
  #removing dollar signs in price
  mutate(price = str_remove(price,"\\$")) %>%
  #remove all trailing whitespace of coulmns  
  mutate(name = str_trim(name ,"both")) %>%
  mutate(price = str_trim(price ,"both")) %>%
  mutate(id = str_trim(id ,"both")) %>%
  mutate(rarity = str_trim(rarity ,"both")) %>%
  #remove all whitespace in id 
  mutate(id = str_remove_all(id," ")) %>%
  #lowercase of card rarity  
  mutate(rarity = str_to_lower(rarity)) 

# converting character type column to numeric
silver_tempest_full <- transform(silver_tempest_full,
                             price = as.numeric(price))

# Remove blank values in id numbers
silver_tempest_full <- silver_tempest_full[!(silver_tempest_full$id ==""),] 
```


```{r dtat_type, echo=FALSE, results='hide',message=FALSE}
#Checks the data type of each column
str(silver_tempest_full)
```


### Getting personal collection of silver tempest data frame collection

```{r}
df_box = read.csv('https://raw.githubusercontent.com/melbow2424/Data-606-Final-Project/main/sword_shield_silver_tempest_booster_box_sample%20-%20Sheet1.csv')

df_confirm = read.csv('https://raw.githubusercontent.com/melbow2424/Data-606-Final-Project/main/sword_shield_silver_tempest_confirm_sample%20-%20Sheet1.csv')

df_packs = read.csv('https://raw.githubusercontent.com/melbow2424/Data-606-Final-Project/main/sword_shield_silver_tempest_booster_packs%20-%20Sheet1.csv')

#Removed a column from the data frame of the booster packs
df_packs <- subset(df_packs, select = -c(X))

# Merging the two data frame together to get full booster box sample
df_full_collection = rbind(df_box, df_confirm, df_packs)
```

### Tidying of personal collection of silver tempest data frames before statistical analysis.

```{r}
df_full_collection <- df_full_collection %>%
  #lowercase of card rarity  
  mutate(card_rarity = str_to_lower(card_rarity)) %>%
  #remove all trailing whitespace of card rarity 
  mutate(card_rarity = str_trim(card_rarity ,"both")) %>%
  #replace holo v rare with holo rare v
  mutate(card_rarity = str_replace_all(card_rarity ,"holo v rare", "holo rare v")) %>%
  #remove all whitespace in id 
  mutate(id = str_remove_all(id," "))
```

### Joining Data Frames Together to Summarize Price Total

```{r}
#Merging data frames by id
df_price <- merge(x = df_full_collection, y = silver_tempest_full, by = "id")
#Removing an error card 177/195. Not in set
df_price <- subset(df_price,id != "177/195")
#Removing column rarity 
df_price <- df_price %>% select(-rarity)
```



```{r}
#str(df_price)

sum(df_price$price)

df_price_over <- subset(df_price,price > 0.50)
df_price_under <- subset(df_price,price <= 0.50)
sum(df_price_under$price)
sum(df_price_over$price)
```
### Profit made from Purchasing Silver Tempest
```{r}
#Booster box cost
booster_box = 125.00
#Elite Trainer box cost (has 8 booster backs)
elite_trainer_box = 35.99
#Booster pack cost
booster_pack = 3.32
#Total spend on cards 
card_spending = booster_box + elite_trainer_box + 22*booster_pack

#Profit made
print(sum(df_price$price)-card_spending)
```


### Linear Regression between Price and Card Rarity

Common cards where ranked number one because they were most frequently pulled from packs. Radiant rare and trainer gallery holo rare v cards were ranked at the same number because the had the same number of times they showed in the sample size. Secret rare was ranked last because it was pulled only once out of 660 card samples. To show linearity better, I also took out an outlier card that was excessively priced from all other cards. 

```{r}
df_price %>%
  count(card_rarity)
df_price_rank <- df_price %>%
  #lowercase of card rarity  
  #mutate(card_rank = dense_rank(-desc(count(card_rarity))))
  mutate(card_rank = case_when(card_rarity == "common" ~ 1,
                           card_rarity == "uncommon" ~ 2,
                           card_rarity == "rare" ~ 3,
                           card_rarity == "holo rare" ~ 4,
                           card_rarity == "holo rare v" ~ 5,
                           card_rarity == "trainer gallery holo rare" ~ 6,
                           card_rarity == "radiant rare" ~ 7,
                           card_rarity == "trainer gallery holo rare v" ~ 7,
                           card_rarity == "ultra rare" ~ 8,
                           card_rarity == "holo rare vstar" ~ 9,
                           card_rarity == "secret rare" ~ 10))
# Removing an card outlier. 
df_price_rank  <- subset(df_price_rank ,id != "186/195")
```


### Linear Regression between Price and Card Rarity Plot
```{r}
#plot(df_price$price, df_price$card_rarity)

#ggplot(data = df_price, aes(x = price, y = card_rarity)) +
#geom_point()

ggplot(data = df_price_rank , aes(x = price, y = card_rank)) +
  geom_jitter(shape = 1)+
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
m_bty <- lm(card_rank~price, data=df_price_rank)
summary(m_bty)
```
```{r}
ggplot(data = m_bty, aes(x = .fitted, y = .resid)) +
geom_jitter(shape = 1) +
geom_hline(yintercept = 0, linetype = "dashed") +
xlab("Fitted values") +
ylab("Residuals")
```



```{r}
qqnorm(m_bty$residuals)
qqline(m_bty$residual)
```


```{r}
# Don't know if this one will work
hist(df_price_rank$card_rank)
```







